Dragonfly Territory Ananlysis

### 2020-11-14 analysis/analysisSS.Rmd
larval data re-added

# Read in Data from BioTime - Single study
## this was downloaded from 'http://biotime.st-andrews.ac.uk/taxa.php?10' on 4 October 2020
## study name == 'The development of dragonfly communities and the consequences of territorial behaviour'
## study ID == ''
## BioTIME does not have an API, making this necessary

@@

>>>>

# Read in Data from BioTime - Adult Single study
# An additional study with damselfly larval data will be read in the same way
## this was downloaded from 'http://biotime.st-andrews.ac.uk/taxa.php?10' on 4 October 2020
## study name == 'The development of dragonfly communities and the consequences of territorial behaviour'
## study ID == ''
## BioTIME does not have an API, making this necessary

@@

# Damselfly Larval Data

larval_data <- read.csv("~/GitHub/rrirfinalproject/larval_data.csv")
